Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-12-03 analysis/paper/paper.qmd
stash

```{r}
#| label: tbl-tcsa-ranges
#| tbl-cap: "TCSA range from Lombard (2021 & 2022)"

# library(gt)
# library(sass)
read_csv(here::here("analysis/data/raw_data/tcsa-range-from-lombard-2022.csv")) %>% 
  knitr::kable(.)
  # gt() %>% 
  # tab_options(row.striping.include_table_body = FALSE) %>%
  # tab_style(
  #   style = cell_borders(
  #     sides = c("top"),
  #     color = "black",
  #     weight = px(3),
  #     style = "solid"
  #   ),
  #   locations = cells_body(
  #     columns = everything(),
  #     rows = c(1)
  #   )
  # ) %>% 
  # tab_options(
  #   table.border.top.style = "hidden",
  #   table.border.bottom.style = "hidden"
  # )
```

>>>>

```{r}
#| label: tbl-tcsa-ranges
#| tbl-cap: TCSA range from Lombard (2021 & 2022)

library(gt)
library(sass)
read_csv(here::here("analysis/data/raw_data/tcsa-range-from-lombard-2022.csv")) %>% 
  gt(caption = "TCSA range from Lombard (2021 & 2022)") %>% 
  tab_options(row.striping.include_table_body = FALSE) %>%
  tab_style(
    style = cell_borders(
      sides = c("top"),
      color = "black",
      weight = px(3),
      style = "solid"
    ),
    locations = cells_body(
      columns = everything(),
      rows = c(1)
    )
  ) %>% 
  tab_options(
    table.border.top.style = "hidden",
    table.border.bottom.style = "hidden"
  )
```
